### 2015-06-25 Manuscript/BiologyLetters/Missing_mammals-draft.tex
Updated ref

#Line numbering
\modulolinenumbers[1]
\linenumbers

@@

\section{Results}
22 of 28 orders have low coverage (\textless 25\% species with cladistic data) and six have high coverage (\textgreater 75\% species with cladistic data) at the species-level.
At the genus-level, three orders have low coverage and 12 have high coverage, and at the family-level, no orders have low coverage and 23 have high coverage (Table \ref{Table_morpho_taxa_proportion}).

@@

Only six orders had significantly clustered data (Afrosoricida and Pholidota at the species-level, and Carnivora, Cetartiodactyla, Chiroptera and Soricomorpha at both species- and genus-level) and none had significantly overdispersed data (Table~\ref{Table_data_structure}).

>>>>

%Line numbering
\modulolinenumbers[1]
\linenumbers

@@

\section{Results}
22 of 28 orders have low coverage (\textless 25\% species with cladistic data) and six have high coverage (\textgreater 75\% species with cladistic data) at the species-level.
At the genus-level, three orders have low coverage and 12 have high coverage, and at the family-level, no orders have low coverage and 23 have high coverage (Table\ref{Table_results}).

%TG: don't clean up this caption please!
%\caption{Number of taxa with available cladistic data for mammalian orders at three taxonomic levels. The left vertical bar represents low coverage (\textless 25\%); the right vertical bar represents high coverage (\textgreater 75\%). Negative Net Relatedness Index (NRI) and Nearest Taxon Index (NTI) values indicate phylogenetic overdispersion; positive values indicate phylogenetic clustering. Significant NRI or NTI values are in bold. *p \textless 0.05; **p \textless 0.01; ***p \textless 0.001.} \\ 
%TG: don't clean up this caption please!

@@

Only six orders had significantly clustered data (Afrosoricida and Pholidota at the species-level, and Carnivora, Cetartiodactyla, Chiroptera and Soricomorpha at both species- and genus-level) and none had significantly overdispersed data (Table~\ref{Table_results}).
